Galois Transformers and Modular Abstract Interpreters:\\ Reusable Metatheory for Program Analysis

### 2014-11-13 writeup/pldi15.tex
Reworking abstract.

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\floatstyle{boxed}
\restylefloat{figure}

@@

%\title{The Marriage of Monad Transformers and Abstract Interpreters: Modular Metatheory for Program Analysis}
\title{Monad Transformers and Modular Abstract Interpreters:\\ Reusable Metatheory for Program Analysis}
\authorinfo{David Darais}{Harvard University, USA}{darais@seas.harvard.edu}
\authorinfo{Matthew Might}{University of Utah, USA}{might@cs.utah.edu}
\authorinfo{David Van Horn}{University of Maryland, USA}{dvanhorn@cs.umd.edu}
\maketitle

@@

The design and implementation of static analyzers have becoming increasingly systematic.
In fact, design and implementation have remained seemingly on the verge of full mechanization for several years.
A stumbling block in full mechanization has been the ad hoc nature of soundness proofs accompanying each analyzer.
While design and implementation is largely systematic, 
  soundness proofs can change significantly with (apparently) minor changes to the semantics and analyzers themselves.
We finally reconcile the systematic construction of static analyzers with their proofs of soundness 
  via a mechanistic Galois-connection-based metatheory for static analyzers.

\end{abstract}
% }-}

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\usepackage{latexsym}
\floatstyle{boxed}
\restylefloat{figure}

@@

%\title{The Marriage of Monad Transformers and Abstract Interpreters: Modular Metatheory for Program Analysis}
\title{Galois Transformers and Modular Abstract Interpreters:\\ Reusable Metatheory for Program Analysis}
\authorinfo{David Darais}{Harvard University, USA}{darais@seas.harvard.edu}
\authorinfo{Matthew Might}{University of Utah, USA}{might@cs.utah.edu}
\authorinfo{David Van Horn}{University of Maryland, USA}{dvanhorn@cs.umd.edu}
\maketitle

@@

The design and implementation of static analyzers have becoming
increasingly systematic.  In fact, design and implementation have
remained seemingly on the verge of full mechanization for several
years.  A stumbling block in full mechanization has been the ad hoc
nature of soundness proofs accompanying each analyzer.  While design
and implementation is largely systematic, soundness proofs can change
significantly with (apparently) minor changes to the semantics and
analyzers themselves.

\par We solve the problem of systematically constructing static
analyzers by introducing the notion of a \emph{Galois transformer}, a
monad transformer that satisfies the properties of a Galois
connection.  In concert with a monadic interpreter, we are able to
define a library of monad transfomers implementing classic context,
path, and heap (in-)senstive building blocks which can be composed
together to realize a program analysis monad, \emph{independent of the
  language being analyzed}.

\par Significantly, a Galois transformer can be proved sound once and
for all, making it a reusable analysis component.  As new analaysis
features and abstractions are developed and mixed in, soundness proofs
need not be reconstructed as the composition of a monad transfomer
stack is sound by virtue of its consituents.  We believe Galois
transformers provide a viable foundation for resuable and composable 
metatheory for program analysis.
\end{abstract}
% }-}
